Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-08 text/src/article.tex
Fix references for background

Scaffolding may be considered a combination of \emph{in vitro} and \emph{in
silico} methods. Several steps may be performed computationally by using
available data to generate a scaffold. Examples may be the use of pair reads
sequencing, where reads a known distance apart, or from comparing contigs to
a reference genome. In the case where \emph{in silico} methods are unable to
complete the scaffold in may be necessary to use PCR to amplify then use
traditional Sanger sequencing to find the sequence and close gaps. Obviously
\emph{in silico} methods are preferable as they less costly in laboratory time
and materials \cite{nagaryan2010}. \pb

For these reason may examples exist for software to generate genome scaffolds
from assembly data. These software use a variety of approaches. Synteny
approaches use a reference genome to order and orient contigs
\cite{richter2007,zhao2008}. Repeat regions which may be responsible for many
of the gaps between contigs may be reassembled using algorithms specifically
for repeat resolution \cite{mulkov2002,koren2010}. Uniquely matching reads may
be used to try and bridge gaps between scaffolds \cite{tsai2010}. Whole genome
may use heuristic graph algorithms to build a path between contigs using
multiple input data \cite{pop2004,dayarian2010}. Finally when the scaffold
cannot be completely resolved \emph{in silico} software packages exist to
suggest the likely primers necessary for determining the sequence in gap
regions \cite{gordon2001,nagaryan2010}. Taken together these tools provide
a wide variety of possible options for scaffolding a genome should an
assembler be unable to produce a continuous sequence from the sequencing
reads. \pb

>>>>

Scaffolding may be considered a combination of \emph{in vitro} and \emph{in
silico} methods. Several steps may be performed computationally by using
available data to generate a scaffold. Examples may be the use of pair reads
sequencing, where reads a known distance apart, or from comparing contigs to
a reference genome. In the case where \emph{in silico} methods are unable to
complete the scaffold in may be necessary to use PCR to amplify then use
traditional Sanger sequencing to find the sequence and close gaps. Obviously
\emph{in silico} methods are preferable as they less costly in laboratory time
and materials \cite{nagarajan2010}. \pb

For these reason may examples exist for software to generate genome scaffolds
from assembly data. These software use a variety of approaches. Synteny
approaches use a reference genome to order and orient contigs
\cite{richter2007,zhao2008}. Repeat regions which may be responsible for many
of the gaps between contigs may be reassembled using algorithms specifically
for repeat resolution \cite{mulyukov2002,koren2010}. Uniquely matching reads
may be used to try and bridge gaps between scaffolds \cite{tsai2010}. Whole
genome may use heuristic graph algorithms to build a path between contigs using
multiple input data \cite{pop2004,dayarian2010}. Finally when the scaffold
cannot be completely resolved \emph{in silico} software packages exist to
suggest the likely primers necessary for determining the sequence in gap
regions \cite{gordon2001,nagarajan2010}. Taken together these tools provide
a wide variety of possible options for scaffolding a genome should an assembler
be unable to produce a continuous sequence from the sequencing reads. \pb
